Precision calculations of the cosmic shear power spectrum projection

### 2017-02-03 limber2.tex
updated figure 2
MK: Update figure

%\input abbr-journals

@@

In Fig.~\ref{fig:Cl_cases} we plot the full shear power spectrum and some of
the approximations. For $\ell > 100$ all power spectra coincide to better than one percent.
The extended first-order Limber approximation shows a better convergence to the true
power spectrum, the error decreases with $\ell^{-2}$. Including the spherical prefactor
decreases the difference by a factor of a few for $\ell < 5$.
Going to second-order yields percent accuracy down to $\ell = 4$.

@@

  \caption{Shear power spectrum for different approximation. Limber to first order: for flat-sky (L1Fl),
        extended ($\ell + 1/2$) for flat sky (ExtL1Fl), and extended in the spherical expansion (ExtL1Sph);
        Second-order extended Limber spherical expansion (ExtL2Sph); full (exact) spherical projection (FullSph).
        The left (right) panels show the total (relative difference) power spectrum.
        See Table \ref{tab:cases} for more details on the different approximations. \mk{Right panel needs to be updated!
        ExtL1Fl curve is actually ExtL1FlHyb.}
      }

@@

  \begin{center}
    \resizebox{1.0\hsize}{!}{
      \includegraphics{figures/xi_p_comp}
      \includegraphics{figures/xi_m_comp}
    }
  \end{center}

  %\caption{Shear correlation funtions $\xi_+$ (\emph{left panel}) and $\xi_-$ (\emph{right}) in the
    %%represenation as in \cite{2016arXiv161104954K}. See Table \ref{tab:cases} for the cases of different
    %approximations and their symbols. The  points with error bars are the data from
    %\cite{CFHTLenS-2pt-notomo}; the theotical predictions correspond to the best-fit parameters with
    %$\Omega_{\rm m} = 0.279$ and $\sigma_8 = 0.79$, except the red dashed curve with adapts a Planck-best fit
    %normalisation $\sigma_8 = 0.83$.}

>>>>

\input abbr-journals

@@

In Fig.~\ref{fig:Cl_cases} we plot the full shear power spectrum and some of
the approximations. For $\ell > 100$ all power spectra coincide to better than
one percent. The standard first-order Limber approximation is better than 10\%
but for the lowest $\ell$, but converges slowly to the true projection to
higher $\ell$. For the extended Limber approximations, despite slightly worse
for $\ell < 10$ in the hybrid cases, the errors with respect to the true power spectrum
decrease much faster, with $\ell^{-2}$.
Including the spherical prefactor decreases the difference by a
factor of a few for $\ell < 5$. Going to second-order yields percent accuracy
down to $\ell = 4$.

The flat extended Limber approximations (ExtL1Fl and ExtL2Fl) perform relatively poorly, and
reach 10\% precision only at $\ell > 100$.

@@

  \caption{Shear power spectrum for different approximation. Limber to first order: standard with flat-sky (L1Fl),
        extended for flat sky (ExtL1Fl), extended hybrid for flat sky (ExtL1FlHyb),
        and extended in the spherical expansion (ExtL1Sph);
        second-order Limber approximations: extended flat sky (ExtL2Fl), extended hybrid flat sky (ExtL2FlHyb),
        and extended spherical expansion (ExtL2Sph); full (exact) spherical projection (FullSph).
        The left panels show the total power spectrum.
        See Table \ref{tab:cases} for more details on the different approximations.
        }

@@

  \begin{center}
    \resizebox{1.0\hsize}{!}{
      \includegraphics{figures/xi_p_comp}
      \includegraphics{figures/xi_m_comp}
    }

    \resizebox{1.0\hsize}{!}{
      \includegraphics{figures/xi_p_delta}
      \includegraphics{figures/xi_m_delta}
    }
  \end{center}

  \caption{Shear correlation funtions $\xi_+$ (\emph{left panels}) and $\xi_-$ (\emph{right}).
    The lower row shows the relative differences to the case Ext2Sph,  see Table \ref{tab:cases} for the different
    approximations and their symbols.
    %\cite{CFHTLenS-2pt-notomo}; the theotical predictions correspond to the best-fit parameters with
    %$\Omega_{\rm m} = 0.279$ and $\sigma_8 = 0.79$, except the red dashed curve with adapts a Planck-best fit
    %normalisation $\sigma_8 = 0.83$.
  }
